### 2025-09-30 cognitive-bias.qmd
20250930 - bye weeks

Focus on the decision-making process when evaluating the quality of decisions, rather than the outcome [@Tanney2021].
Yes, also evaluate the outcomes of decisions, but do not give yourself too much credit for lucky decisions or too much blame for unlucky decisions (like injuries).
Luck is going to happen.
If you are making optimal decisions that maximize the expected value of returns (e.g., projected fantasy points), you are following a strong process.
That said, one thing you can count on is that players get injured.
So, it is to your benefit to draft and compose your team to have some bench depth so you can handle injuries when they inevitably occur.

>>>>

Focus on the decision-making process when evaluating the quality of decisions, rather than the outcome [@Tanney2021].
Yes, also evaluate the outcomes of decisions, but do not give yourself too much credit for lucky decisions or too much blame for unlucky decisions (like injuries).
Luck is going to happen.
If you are making optimal decisions that maximize the expected value of returns (e.g., projected fantasy points), you are following a strong process.
That said, one thing you can count on is that players get injured and have bye weeks.
So, it is to your benefit to draft and compose your team to have some bench depth so you can handle injuries and bye weeks when they inevitably occur.

### 2025-09-30 draft.qmd
20250930 - bye weeks

An alternative to the "stars and scrubs" approach is to wait to draft more "high-value" players after other managers have over-paid for players.
In any case, having some small amount of cap left over toward the end of the draft can help you draft good value players to fill out your bench spots for cheap (e.g., $2).
Having some depth can help you offset the risk of injuries and the possibility that some of your starters may underperform their expectation, which is quite likely given how [challenging it is to predict fantasy performance](#sec-accuracyOfCrowd).

>>>>

An alternative to the "stars and scrubs" approach is to wait to draft more "high-value" players after other managers have over-paid for players.
In any case, having some small amount of cap left over toward the end of the draft can help you draft good value players to fill out your bench spots for cheap (e.g., $2).
Having some depth can help you offset the impacts of bye weeks, the risk of injuries, and the possibility that some of your starters may underperform their expectation, which is quite likely given how [challenging it is to predict fantasy performance](#sec-accuracyOfCrowd).
